\section{Project Experience}
% \cventry
% {Stable Diffusion Image Generation Model Fine Tuning} % Job Title
% {Undergraduate Research Opportunity(UROP)} % Organization
% {HKUST} % Location
% {2024.2 - 2024.5} % Date
% \begin{cvitems}
% \item {Fine-tuned a Stable Diffusion image generation model using LoRA, achieving improved style adaptation. Further enhanced generation stability and controllability by integrating ControlNet for precise conditioning.}
% \end{cvitems}

\cventry
{Undergraduate Research Opportunity (UROP)} % Job Title
{LLM Agent Development} % Organization
{Supervised by Prof. Shenghui Song} % Location
{Jun 2024 - Present} % Date
\begin{cvitems}
\item {Designed and implemented a Large Language Model (LLM) agent capable of playing board games. Conducted comprehensive evaluations of agent strategies and performance.}
\end{cvitems}

\cventry
{Course Project} % Job Title
{Mobile Robot Algorithm Implementation} % Organization
{Supervised by Prof. Shaojie Shen} % Location
{Sep 2024 - Dec 2024} % Date
\begin{cvitems}
\item {Developed mobile robot algorithms from scratch, including ICP Odometry, EKF SLAM, and A* path planning within a simulation environment, enabling robust localization (localization error < 1cm), mapping, and navigation.}
\end{cvitems}

\cventry
{Research Practicum} % Job Title
{Quadruped Robot Control} % Organization
{Supervised by Prof. Maurice Pagnucco and Prof. Yang Song} % Location
{Feb 2025 - Aug 2025} % Date
\begin{cvitems}
\item {Built and programmed a Unitree GO2 quadruped robot to perform complex tasks, integrating depth camera for accurate object localization (localization error < 10cm) and LiDAR for SLAM.}
\end{cvitems}

\cventry
{Final Year Project} % Job Title
{Underwater Localization System} % Organization
{Supervised by Prof. Huan Yin and Prof. Fumin Zhang} % Location
{Jun 2025 - Present} % Date
\begin{cvitems}
\item {Developed a Multi-Camera Vision-Based Localization System for Tracking Multiple Autonomous Underwater Vehicles (AUVs). Reduced localization error in complex underwater lighting scenarios, improving positioning accuracy to within 10cm in a 1m$\times$1m range.}
\end{cvitems}